---
title: "Yap's R Cookbook"
---

Hello, Website!

### 


### keyboard shortcuts

control-shift-m is the keyboard shortcuts for 'Pipe.'
![](https://pbs.twimg.com/media/El-mdoEXIAAHJ6y?format=jpg&name=small)

### Creating my First Package
```{r}


```

### Dates


    Use str() to look at the structure of x and confirm it is just a character string

    Convert x to a date using as.Date()

    Use str() to look at the structore of x_date and confirm it is a Date

    Now, use as.Date() to store the date April 10, 2014
    
```{r}
# The date R 4.0.0 was released
x <- "2020-04-24"
# Examine structure of x
str(x)
```
```{r}
# Use as.Date() to interpret x as a date
x_date <- as.Date(x)

# Examine structure of x_date
str(x_date)
```
### Instructions:

- Use read_csv() to read in the CSV file rversions.csv as releases

- Use str() to examine the structure of the date column

- anytime package is loaded and created an object called sep_10_2009. Use the anytime() function to parse sep_10_2009


```{r}
# Load the readr package
library(readr)

# Use read_csv() to import rversions.csv
releases <- read_csv("https://assets.datacamp.com/production/course_5348/datasets/rversions.csv")
```

```{r}

# Examine the structure of the date column
str(releases$date)    
```
### Plotting

Instructions:

    Make a plot of releases over time by setting the x argument of the aes() function to the date column

    Zoom in to the period from 2010 to 2014 by specifying limits from “2010-01-01” to “2014-01-01”. (Note: These strings need to be wrapped in as.Date() to be interpreted as Date objects)

    Adjust the axis labeling by specifying date_breaks of “10 years”and date_labels of “%Y”
    
```{r}
library(ggplot2)

# Set the x axis to the date column
ggplot(releases, aes(x = date, y = type)) + 
  geom_line(aes(group = 1, color = factor(major)))
```

```{r}

```
    
